%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript 
% font uncomment this line and comment the one above
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{soul}
%\pgfplotsset{width=7cm,compat=1.8}

\newsectionwidth{0pt} % Stops section indenting
\hypersetup{
	colorlinks   = true, %Colours links instead of ugly boxes
	urlcolor     = blue, %Colour for external hyperlinks
	linkcolor    = green, %Colour of internal links
	citecolor   = blue %Colour of citations, could be ``red''
}
\pagestyle{plain}
\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------
\begin{center}
	{\large{\bf{\textsc{Agung Prakasya}}}}\\
	\vspace{16pt}
	{\small \href{mailto:aprksy@gmail.com}{aprksy@gmail.com}; 
	\href{https://wa.me/628197519750}{+62 8-1975-1975-0}; 
	\href{https://www.linkedin.com/in/agungprakasya/}{linkedin}; 
	\href{https://github.com/aprksy}{github};\\
	Jakarta, Indonesia; UTC +7:00;}
\end{center}

% Your address 1
\begin{resume}
\vspace{-10pt}
%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
\begin{multicols}{2}
\section{\centerline{personal info}}
\vspace{8pt} % Gap between title and text
\emph{Born}: Ciamis, 20 May 1975\\Live in Jonggol, West Java, Indonesia\\\emph{Nationality}: Indonesian
\columnbreak
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{education}}
\vspace{-10pt} % Gap between title and text
\begin{flushright}
	\emph{Degree in Math (2000)}\\
Math Dept. of Institut Teknologi Bandung\\ 
Majoring in \emph{Computational Math Modelling}
\end{flushright}
\end{multicols}
%----------------------------------------------------------------------------------------
\vspace{-30pt}
\begin{center}
	\rule{0.5\textwidth}{1pt}
\end{center}

\begin{quotation}
	{\large 
	\emph{23 Years} of total experience; 23\texttt{+} years of coding in various languages; 
	8 years in \emph{bigdata and data-streams}; 
	11 years of experience in energy and other industries ---mostly on
	\emph{engeering, solution architect} \& \emph{specialist position}};
\end{quotation}
\vspace{-20pt}
\begin{center}
	\rule{0.5\textwidth}{1pt}
\end{center}
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
%\vspace{12pt}
\begin{multicols}{2}
\section{\centerline{qualification}}
\vspace{8pt} % Gap between title and text
\emph{Builds trusts} -- \emph{guides} -- \textit{inspires} -- \emph{leads} team; Anticipates technology trends/change; 
Mixes \& matches personnels to achieve effective team composition; 
\emph{Polyglot coder} (Go, C/C\texttt{++}, Delphi/Pascal etc); 
A long-time \emph{Linux}/BSD cli-er; \emph{systematic} problem solving, 
\emph{Statistical} data analysis and \emph{Math} modelling.
Love to learn new things.

%----------------------------------------------------------------------------------------
\columnbreak
%\vspace{0.2in} % Some whitespace between sections
%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{experience}}
\vspace{8pt} % Gap between title and text
\textbf{Implements} \emph{\href{https://www.imsglobal.org/spec/lti/v1p3}{LTI 1.3 Core}} and Partial \emph{\href{https://www.nist.gov/system/files/documents/itl/ansi/Approved-Std-20070427-2.pdf}{American National Standard for
Information Systems --Data Format for the Interchange of Fingerprint, Facial, \& Other Biometric Information}}.
\textbf{Architected} \emph{Massive} text raw data processing using \emph{Go} and Linux Standard Tools;
Realtime Core-banking offloading using\emph{Confluent Kafka} streams;
Bigdata migration to \emph{Hadoop} using \emph{Sqoop} and \emph{Talend};
Industrial \emph{\href{https://en.wikipedia.org/wiki/SCADA}{SCADA}--enterprise} integration using \href{https://opcfoundation.org}{OPC} protocol; 

\end{multicols}

\vspace{-30pt}
\begin{center}
	\rule{0.5\textwidth}{1pt}
\end{center}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SKILL SECTION
%----------------------------------------------------------------------------------------
	
	\section{\centerline{Personal Research}}
	\vspace{8pt} % Gap between title and text
	Design and write an Extended \emph{\href{https://en.wikipedia.org/wiki/Petri_net}{Petrinet}} library ---to support \emph{types}, \emph{timings} and \emph{cost}, 
	for dynamic system modelling (\emph{work-in-progress}, \emph{Go}); 
	Perform Proof of Concept for High Performance Toolset Architecture for Massive Text Data (\emph{work-in-progress}, \emph{C\texttt{++}}); 
	Design an \emph{Elastic Ring} data type for incomplete image \emph{congruence detection} 
	(postponed, need to proof some theorems first); 
	\begin{center}
		\rule{0.5\textwidth}{.2pt}
	\end{center}
	\pagebreak

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{PROFESSIONAL EXPERIENCE}} 
%----------------------------------------------------------------------------------------
\vspace{16pt} % Gap between title and text
\begin{minipage}{6cm}
\begin{flushright}
	{\bf \href{https://quipper.com}{Quipper}} \\
	{\footnotesize{\sl June 2022--Present}}\\
	{\footnotesize{\sl Remote}}\\
	{\bf Solution Architect} \\
	{\footnotesize reports to: Lead Solution Architect} \\
	{\footnotesize team: \emph{none}}
\end{flushright}
\end{minipage}
\hspace{1cm}
\begin{minipage}{0.59\linewidth}
	Research \& Design architecture for products, and propose transition phases. Perform pioneering on RFC/
	Standards/Specification implementation, consolidate requirements including timelines and convert to actionable 
	items for used by development team. Perform strategic developments, by means of determine technology which will be use often, 
	develop libraries and perform internal PoCs.
\end{minipage}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}
%----------------------------------------------------------------------------------------
\vspace{16pt} % Gap between title and text
\begin{minipage}{0.59\linewidth}
	Designed architectural customizations for company product to suit client needs. 
	Adopted new technology for product development. Lead team in project delivery. 
	Determine tools both for internal use and to be proposed for using in projects.
	Together with Sales and Pre-sales team performed project initialization preparation.
\end{minipage}
\hspace{1cm}
\begin{minipage}{6cm}
	{\bf \href{https://paques.id}{Paques}}\\
	{\footnotesize{\sl February 2021--June 2022}} \\
	{\footnotesize{\sl Hybrid/Jakarta}} \\
	{\bf Senior Engineer} \\
	{\footnotesize reports to: Engineering Manager} \\
	{\footnotesize team: \emph{6 persons (project team)}}
\end{minipage}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}
%----------------------------------------------------------------------------------------
\vspace{16pt} % Gap between title and text
\begin{minipage}{6cm}
\begin{flushright}
	{\bf \href{https://sibernetik.co.id}{Sibernetik}} \\
	{\footnotesize{\sl Dec 2017--Jan 2021}}\\
	{\footnotesize{\sl Hybrid/Jakarta}}\\
	{\bf Senior Engineer} \\
	{\footnotesize reports to: Engineering Manager} \\
	{\footnotesize team: \emph{3 persons}}
\end{flushright}
\end{minipage}
\hspace{1cm}
\begin{minipage}{0.59\linewidth}
	Architected solutions to suit client needs. 
	Adopted new technology for product development. 
	Lead team in project delivery. 
	Determine tools both for internal use and to be proposed for using in projects.
	Together with Sales and Pre-sales team performed project initialization preparation.
\end{minipage}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}
%----------------------------------------------------------------------------------------
\vspace{16pt} % Gap between title and text
\begin{minipage}{0.59\linewidth}
	Designed multiple big data architecture for various cases. 
	Build teams for project according to requirements.
	Determine tools both for internal use and to be proposed for using in projects.
	Together with Sales and Pre-sales team performed project initialization preparation.
\end{minipage}
\hspace{1cm}
\begin{minipage}{6cm}
	{\bf \href{https://dattabot.io}{Dattabot}}\\
	{\footnotesize{\sl Aug 2016--Dec 2017}} \\
	{\footnotesize{\sl Jakarta}} \\	
	{\bf Senior Engineer} \\
	{\footnotesize reports to: Engineering Manager} \\
	{\footnotesize team: \emph{none}}
\end{minipage}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}
%----------------------------------------------------------------------------------------
\vspace{16pt} % Gap between title and text
\begin{minipage}{6cm}
	\begin{flushright}
		{\bf Dowedo} \\
		{\footnotesize{\sl Sep 2014--Dec 2016}}\\
		{\footnotesize{\sl Hybrid/Jakarta}}\\
		{\bf CTO, Co-founder} \\
		{\footnotesize reports to: CEO} \\
		{\footnotesize team: \emph{3 persons}}
	\end{flushright}
\end{minipage}
\hspace{1cm}
\begin{minipage}{0.59\linewidth}
	Determined technology both to develop product and platform.
	Determined milestone for product development.
	Determined team capability and skill set requirements.
	Determined tools both for internal use and to be proposed for using in projects.
\end{minipage}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}
%----------------------------------------------------------------------------------------
\begin{quotation}
	\begin{center}
		{\large First 13 years experience summary}
	\end{center}
	\vspace{10pt} % Gap between title and text
	Most years were at energy sectors (oil, gas and coal).
	Had been working for \href{https://siemens.co.id}{Siemens} and done work for projects and provide professional services at oil 
	companies \href{https://totalenergies.id}{Total E\&P Indonésie}, \href{https://pertamina.com}{Pertamina}, gas company \href{https://pgn.co.id}{PGN}, 
	coal mining company \href{https://kpc.co.id}{KPC} and transporter company \href{https://elnusapetrofin.co.id}{Petrofin}.
	Had been using various technology, Delphi, C\texttt{++}, DCOM, C\texttt{\#}, Visual Basic, PHP and open standard like \href{https://opcfoundation.org}{OPC}.

\end{quotation}
%----------------------------------------------------------------------------------------
\begin{center}
	\rule{0.5\textwidth}{1pt}
\end{center}
%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTERESTS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
coding, math, guitar \& basses, woodworking, gardening
\end{center} 

%----------------------------------------------------------------------------------------
\end{resume} 

\end{document}