%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript 
% font uncomment this line and comment the one above
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{soul}
\usepackage{pgfplots}
%\pgfplotsset{width=7cm,compat=1.8}

\newsectionwidth{0pt} % Stops section indenting
\hypersetup{
	colorlinks   = true, %Colours links instead of ugly boxes
	urlcolor     = blue, %Colour for external hyperlinks
	linkcolor    = green, %Colour of internal links
	citecolor   = blue %Colour of citations, could be ``red''
}
\pagestyle{plain}
\begin{document}

\begin{center}
	\textsc{Agung Prakasya}

	\textbf{{\scriptsize email}}. \href{mailto:aprksy@gmail.com}{aprksy@gmail.com}; 
	\textbf{{\scriptsize phone}}. \href{https://wa.me/628197519750}{+62 8-1975-1975-0};\\ 
	\textbf{{\scriptsize linkedIn}}. \href{https://www.linkedin.com/in/agungprakasya/}{linkedin.com/in/agungprakasya/}\\ 
	\textbf{{\scriptsize github}}. \href{https://github.com/aprksy}{github.com/aprksy}
\end{center}


\vspace{-20pt}
\begin{center}
	\rule{0.5\textwidth}{1pt}
\end{center}

To: Hiring team
at \href{https://level.io/}{Level.io}

Hi there, how are you today? Fine here.
Let me first introduce myself, my name is \textit{Agung Prakasya}, and I’m writing this letter to
show you my interest in the position you’re offering.

I’m currently working at \href{https://www.quipper.com}{\textit{Quipper}}, an ed-tech company, as a solution architect. I graduated
from the Math dept. at \href{https://www.itb.ac.id}{\textit{Bandung Institute of Technology}} and have 15+ years of experience
which hopefully —in this quickly evolving technology age— is still relevant.

I use Go and Linux standard tools in my last 6 years of work, mainly for concurrent data
processing and microservices. I’m currently updating my C++ knowledge to 17/20 and
learning Rust, V \& Elixir. Before that, I used Delphi, C/C++, and a little bit of Python,
PHP and Java. Please refer to my resume for more details, hopefully, you can find something
of interest for your team.

I am interested to apply here because Level.io is a small team, and I think it’s a good fit for
me. And the advertisement also catching, it’s specific and clear while staying humble. Aside
from that, with the aforementioned technicalities I’m confident to be able to contribute to the
team. I’ve been working with Win32 API for about 10 years. And for IPC, under Windows, I
have worked with DCOM and OLE technology, while in Linux I used sockets, shared memory, and pipes, and used named pipes for both.

In my current job, one of my tasks is to implement a standard namely \href{https://www.imsglobal.org/spec/lti/v1p3}{LTI 1.3} and translate it
to workable items, pioneering the development process until it reached a stable state and
handed over to the team. I’m sure I can catch up with the standard being used by the team
and also would be happy to learn/share new things from/to the team.

I apologize for this lengthy email, but I hope you can understand. If you find something you
would like to know more about, please don’t hesitate to contact me. Thank you.

Sincerely,\\
\textbf{Agung Prakasya}


\pagebreak

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------
\name{\textsc{Agung Prakasya}\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{\textbf{{\scriptsize email}}. \href{mailto:aprksy@gmail.com}{aprksy@gmail.com}; 
\textbf{{\scriptsize phone}}. \href{https://wa.me/628197519750}{+62 8-1975-1975-0};\\ 
\textbf{{\scriptsize linkedIn}}. \href{https://www.linkedin.com/in/agungprakasya/}{linkedin.com/in/agungprakasya/}\\ 
\textbf{{\scriptsize github}}. \href{https://github.com/aprksy}{github.com/aprksy}}
% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

% Your address 1
\begin{resume}
\vspace{20pt}
%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
\begin{multicols}{2}
\section{\centerline{personal info}}
\vspace{8pt} % Gap between title and text
\emph{Born}: Ciamis, 20 May 1975\\Live in East of Cibubur, West Java\\\emph{Nationality}: Indonesian
\columnbreak
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{education}}
\vspace{-10pt} % Gap between title and text
\begin{flushright}
	\emph{Degree in Math (2000)}\\
Math Dept. of Institut Teknologi Bandung\\ 
Majoring in \emph{Computational Math Modelling}
\end{flushright}
\end{multicols}
%----------------------------------------------------------------------------------------
\vspace{-30pt}
\begin{center}
	\rule{0.5\textwidth}{1pt}
\end{center}

\begin{quotation}
	{\large \emph{23 Years} of total experience; 23+ years of coding in various languages; 17 years in various 
	\emph{distributed systems}; 8 years in \emph{bigdata and datastreams}; 
	11 years of experience in energy and other industries ---mostly on
	\emph{project management, solution architect} \& \emph{specialist position}};
\end{quotation}
\vspace{-20pt}
\begin{center}
	\rule{0.5\textwidth}{1pt}
\end{center}
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
%\vspace{12pt}
\begin{multicols}{2}
\section{\centerline{qualification}}
\vspace{8pt} % Gap between title and text
\emph{Builds trusts}, \emph{guides}, inspiration \emph{wannabe} \& leads team; Anticipates technology trends/change; 
Manages team of large size and/or high-skilled personnels; Mixes \& matches personnels to achieve effective team composition; 
\emph{Polyglot coder} (Go, C/C++, Delphi/Pascal, C\#, etc); 
A long-time \emph{Linux/BSD cli-er}; Very good on analysis and \emph{systematic problem solving}, 
\emph{statistical data analysis} and \emph{math modelling}.\\
Love to learn new things.

%----------------------------------------------------------------------------------------
\columnbreak
%\vspace{0.2in} % Some whitespace between sections
%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{experience}}
\vspace{8pt} % Gap between title and text
Managed large \emph{multi-sites} (Java, Sumatera, Kalimantan, Sulawesi \& Bali) team of 150s persons, 
including developers, operators and managers for a 3 years managed service project; 
Managed a team of 3 exceptionally high skilled personnels for a \emph{nationwide project};
Architected various systems: \emph{Industrial distributed system}, \emph{SCADA--enterprise integration}, 
\emph{bigdata migration}, nationwide \emph{distributed biometric matching system}, \emph{data-streams}.
\end{multicols}

\vspace{-30pt}
\begin{center}
	\rule{0.5\textwidth}{1pt}
\end{center}
%\centerline{\emph{Expertise vs Production Delivery vs Research of a few technology}}
%\resizebox{!}{2in}{%
%\begin{tikzpicture}
%	\begin{axis}[
%		width=1.7\textwidth,
%		height=0.5\textwidth,
%		ybar,
%		enlargelimits=0.1,
%		legend columns=-1,
%		legend style={at={(0.5,-0.15)},
%			anchor=north,/tikz/every even column/.append style={column sep=0.5cm}},
%		%ylabel={expertise level},
%		symbolic x coords={Go, Pascal, C/C++, Dart/Flutter, Java, C\#, NodeJS, Python, V, Kafka, Hadoop},
%		xtick=data,
%		nodes near coords,
%		nodes near coords align={vertical},
%		]
%		\addplot coordinates {(Go,9) (Pascal,9) (C/C++,7) (Dart/Flutter,7) (Java,7) (C\#,6) (NodeJS,7) (Python,6) (V,8) (Kafka,7) (Hadoop,6)};
%		\addplot coordinates {(Go,8) (Pascal,10) (C/C++,5) (Dart/Flutter,5) (Java,4) (C\#,3) (NodeJS,5) (Python,1) (V,0) (Kafka,5) (Hadoop,2)};
%		\addplot coordinates {(Go,9.5) (Pascal,4) (C/C++,6) (Dart/Flutter,7) (Java, 4) (C\#,2) (NodeJS,6) (Python,3) (V,6) (Kafka,3) (Hadoop,1)};
%		\legend{expertise, production delivery, research}
%	\end{axis}
%\end{tikzpicture}
%}
%----------------------------------------------------------------------------------------
%	PROFESSIONAL SKILL SECTION
%----------------------------------------------------------------------------------------
\pagebreak
\section{\centerline{Programming \& Development}} 

\begin{multicols}{2}
	\vspace{8pt} % Gap between title and text
	\textbf{Built for Productions}:
	\begin{itemize}
		\item \emph{LTI 1.3 Core \& Advantage} Implementation; 
		{\footnotesize \textbf{tags:} Go}
		\item \emph{Big Data}; \emph{Text Processing;}
		{\footnotesize \textbf{tags:} Go, Linux Standard Tools, Awk}
		\item \emph{Microservices}; \emph{API Gateways}; \emph{Dashboards};
		{\footnotesize \textbf{tags:} Go, Node.js}
		\item \emph{\href{https://www.nist.gov/services-resources/software/nist-biometric-image-software-nbis}{NIST} format encoder/decoder}; \emph{\href{https://www.nist.gov/system/files/documents/itl/ansi/sp500-245-a16.pdf} {biometric image format} validator}; built a massive volume (terabytes) \emph{biometric image processing service}. {\footnotesize \textbf{tags:} Go C}
		\item \emph{Android applications}; \emph{Web applications};
		{\footnotesize \textbf{tags:} Flutter, Node.js}
		\item \emph{Industrial distributed system}; \emph{Industrial data communication}; \emph{Industrial software plugins};
		{\footnotesize \textbf{tags:} C++, Delphi, \href{https://opcfoundation.org}{OPC}, \href{https://modbus.org}{Modbus}}
		\item \emph{Data visualization}; \emph{Document/report generator};
		{\footnotesize \textbf{tags:} D3.js}, Ms.Office Automation, \LaTeX
	\end{itemize}
	\textbf{Personal Research}:
	\begin{itemize}
		\item Extended \emph{Petrinet} library, for dynamic system modelling; {\footnotesize \textbf{tags:} Go, V}
		\item High Performance Toolset for Massive Text Data; {\footnotesize \textbf{tags:} C++}
		\item \emph{Elastic Ring} data type for incomplete image \emph{congruence detection}; {\footnotesize \textbf{tags:} Algorithm, Datatype}
	\end{itemize}
\end{multicols}

%Worked intensively with \emph{Git}, \emph{Docker}, \emph{Kafka}, \emph{Postgres}, \emph{NATS}, \emph{Redis}, \emph{Hadoop}, \emph{Cassandra}, \emph{Ms SQL Server}, \emph{CouchDB}, \emph{ArangoDB}, \emph{CockroachDB}, \emph{K3s Kubernetes}, \emph{Google Cloud}, \emph{AWS}, \emph{Azure}, \emph{Siemens WinCC}.

%Currently exploring some other programming language \emph{DigitalMars D}, \emph{Haskell}, \emph{V language}, \emph{Zig}, \emph{Nim}, \emph{Pony} and \emph{Chapel}.

\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{16pt} % Gap between title and text
{\bf \uppercase{Quipper Edukasi Indonesia} (\href{https://quipper.com}{quipper.com})--Jakarta} \hfill {\sl June 2022--Present} \\
{\bf Title: Solution Architect} 

\vspace{10pt} 
\begin{description}
	\item[{\sl {\footnotesize Research \& Design}.}] 
	Research \& Design architecture for products, and propose transition phases to VPoE in adopting new architectures/technologies/approaches.
	\item[{\sl {\footnotesize Adopting Standards}.}] 
	Perform pioneering on RFC and Standards implementation, consolidate requirements including timelines and convert to actionable items for used by development team. 
	\item[{\sl {\footnotesize Strategic Development}.}] 
	Perform strategic developments, by means of determine technology which will be use often, develop libraries and perform internal PoCs.
\end{description}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}

\vspace{16pt} % Gap between title and text
{\bf \uppercase{Informatika Solusi Bisnis} (\href{https://paques.id}{paques.id})--Jakarta} \hfill {\sl February 2021--June 2022} \\
{\bf Title: Senior Engineer} 
Design solution architecture both for products and projects custmized for users.

\vspace{10pt} 
\begin{description}
	\item[{\sl {\footnotesize Q4.2021 - Q2.2022}.}] {\bf Architected Telkomsel Big Data Processing}\hfill {\sl Solution Architect}\\
	To provide a solution for data processing and analytics for communication data in Telkomsel. The solution to date, has been
    processing 50TB data per day and will grow to 90TB per day in Q1 2022.
	\item[{\sl {\footnotesize Q4.2021}.}] {\bf Architected Solution for DSS Bursa Efek Indonesia}\hfill {\sl Solution Architect}\\
	To provide a solution for upgrading the DSS system of Bursa Efek Indonesia.
	\item[{\sl {\footnotesize Q2-Q3.2021}.}] {\bf Architected Solution for Lab. Cyber--Kejagung}\hfill {\sl Solution Architect}\\
	To provide a solution for data processing and analytics for various data including reports, lawful intercepts, oneline news and social
    media.
	\item[{\sl {\footnotesize Q1.2021}.}] {\bf Rearchitected Paques Media Intelligence engine}\hfill {\sl Solution Architect}\\
	To provide a more performant, flexible and bullet-proof internal engine for Paques Media Intelligence, including
    {\sl online-news crawler}, {\sl NLP module} and {\sl FTS services}.
\end{description}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}

{\bf \uppercase{Sibernetik Integra Data} (\href{https://sibernetik.co.id}{sibernetik.co.id})--Jakarta} \hfill {\sl Dec 2017--Jan 2021} \\
{\bf Title: Senior Engineer} 
Determines company's technology related strategies\hfill {\sl Head of Solution Dev.}\\including technology roadmap, acquisition model, stacks, team skill sets requirements and partnerships.

\vspace{10pt} 
\begin{description}
	\item[{\sl {\footnotesize Q1.2020}.}] {\bf Realtime core banking off-loading--BTPN Syariah}\hfill {\sl Solution Architect}\\
	To provide tools and mechanism to BTPN Syariah to perform realtime data off-loading from their T24 core banking system to surrounding application using Attunity and Kafka.
    \item[{\sl {\footnotesize Q4.2019}.}] {\bf Information War Campaign--BSSN}\hfill {\sl Technology Advisor}\\
    To provide media monitoring tools to BSSN regarding issues in social and formal media. Functions: {\sl Sentiment analysis}, bot detection,
    social media monitoring, etc.
    \item[{\sl {\footnotesize Q4.2019}.}] {\bf Sistem Koordinasi Terpadu CAKRA--KOSTRAD}\hfill {\sl Technology Advisor}\\
    To provide media monitoring tools to KOSTRAD regarding issues in social and formal media, personnel distribution, war and peace strategies etc.
    Functions: {\sl Sentiment analysis}, social media monitoring, etc.
    \item[{\sl {\footnotesize 2019--2020}.}] {\bf Bigdata \& Datastreaming Integration\hfill {\sl Technology Advisor}\\--Commonwealth Bank}\\
    To provide {\sl Confluent Kafka} data streaming solution to Commonwealth Bank Digital Banking. Functions: Realtime notification, realtime data ingestion, etc.
    \item[{\sl {\footnotesize 2019--2022}.}] {\bf Bigdata \& Datastreaming Integration--BRI} \hfill {\sl Senior Solution Architect}\\
    To provide {\sl Confluent Kafka} data streaming solution to BRI Digital Banking. Functions: Realtime notification, realtime data ingestion, fraud detection,
    cash management, etc.
    \item[{\sl {\footnotesize Q3.2019}.}] {\bf AIS live data streaming to Bigdata integration\hfill {\sl Technology Advisor}\\--Ditjen Bea Cukai}\\
    To provide {\sl Confluent Kafka} data streaming solution to Ditjen Beacukai. Functions: Realtime AIS data streaming from multiple sources, on the fly data query,
    on the fly data quality etc.
    \item[{\sl {\footnotesize Q1--Q3.2019}.}] {\bf Develop Marine Monitoring--MVP} \hfill {\sl Technology Advisor}\\
    To build an MVP of B2B product, including determining data vendor, technology stack and developing team for building the product.
    \item[{\sl {\footnotesize Q1.2019}.}] {\bf Operational Dashboard--BAKAMLA} \hfill {\sl Technology Advisor}\\
    To provide dashboard solution to BAKAMLA for their strategic and day-to-day operation. Functions: Realtime notification, organizer, maps etc.
    \item[{\sl {\footnotesize Q1.2019}.}] {\bf Ceria Payment Gateway--BRI} \hfill {\sl Technology Advisor}\\
    To implement in-merchant-app payment page and BRI side gateway for BRI ceria microloan.
    \item[{\sl {\footnotesize Q4.2018}.}] {\bf Ceria Collection System--BRI} \hfill {\sl Technology Advisor}\\
    To design \& implement collection system for BRI Ceria, a microloan for online merchant's customers.
    \item[{\sl {\footnotesize Q4.2018}.}] {\bf Ceria Merchant Dashboard--BRI} \hfill {\sl Technology Advisor}\\
    To design \& implement dashboard for BRI merchant (at the time this was written {\sl Tokopedia \& Panorama})
    \item[{\sl {\footnotesize 2017--2018}.}] {\bf Distributed Biometric Matching System\hfill {\sl Solution Architect, PM, Dev}\\--Ditjen Imigrasi}\\
    To design \& implement distributed biometric matching service for other subsystems in SIMKIM v.2 of Ditjen Imigrasi such as Izin Tinggal, Visa, Layanan Paspor, Cekal etc.
\end{description}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}

{\bf \uppercase{Mediatrac Sistem Komunikasi} (\href{https://dattabot.io}{dattabot.io})--Jakarta} \hfill {\sl Aug--Dec 2017} \\
{\bf Title: Senior Engineer} 
To determine bigdata architecture and data migration methodology \hfill {\sl Consultant}

\vspace{10pt} 
\begin{description}
    \item[{\sl {\footnotesize Q3--Q4.2017}.}] {\bf Bigdata migration--Bank Danamon}\hfill {\sl Sr. Solution Architect}\\
    This project was to perform data migration from various data sources and core banking system to client's new data warehouse. This project
    employ various technologies such as {\sl Cloudera Hadoop}, {\sl Talend}, {\sl Sqoop} etc.
\end{description}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}

{\bf \uppercase{Dowedo}--Jakarta} \hfill {\sl Sep 2016--Jan 2018} \\
To design system architecture and implement Online Tourism\hfill {\sl Consultant}\\eCommerce platform 

\vspace{10pt} 
\begin{description}
    \item[{\sl {\footnotesize 2016--2018}.}] {\bf Building Tourism eCommerce Platform}\hfill {\sl Solution Architect}\\
    This project was to build tourism e-Commerce platform. However the life cycle was ended when it reached MVP.
\end{description}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}

{\bf \uppercase{TRIPATRA ENGINEERS \& CONSTRUCTORS}--Jakarta} \hfill {\sl Nov 2013--Apr 2015} \\[2pt]
{\bf Title: Senior Engineer} 
To ensure that project support systems keep aligned with all project \hfill {\sl Sr. Engineer}\\
requirements despite characteristics difference between projects.

\vspace{10pt} 
\begin{description}
    \item[{\sl {\footnotesize Q3.2014}.}] {\bf Electronic Document Management System (EDMS)\hfill {\sl Project Manager}\\--Internal project}\\
    This internal project objective was to develop a new major release of the system. The new release
    was the result of knowledge absorption from on going projects to keep the system
    aligned with future projects requirements.
    \item[{\sl {\footnotesize Q2.2014}.}] {\bf Issue Management System--Internal project}\hfill {\sl Project Manager}\\
    This internal project objective was to develop a system to manage projects issues. The main purpose of the system is, to track issue statuses, 
    expedite for issue solutions and manage issue solution as lesson learned. 
    \item[{\sl {\footnotesize Q1.2014}.}] {\bf Project Control Portal--Internal project}\hfill {\sl Project Manager}\\
    This internal project objective was to develop a centralized information service for the corporate on all projects project control. 
    With this system, corporate are able to track progress status of the on going projects.
\end{description}
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}
 
{\bf \uppercase{Sintesa Solusi Utama}--Java, Kalimantan, Sumatera} \hfill {\sl Feb 2006--Jun 2013} \\
It was a self-owned company which was founded as information technology service provider.

\vspace{10pt} 
\begin{description}
    \item[{\sl {\footnotesize 2007--2013}.}] {\bf Fuel Distribution Management System}\hfill {\sl Project Manager}\\({\sl Java, Sumatera})--{\bf Elnusa Petrofin}\\
    This project was a managed service which provide IT service for client's whole fuel distribution operation, including IT systems, infrastructures
    and human resources.
    \item[{\sl {\footnotesize Q3.2007}.}] {\bf Interactive 3D simulation of Sidoarjo Mud Burst\hfill {\sl Project Manager}\\--Lapindo Brantas}\\
    The project was to build interactive 3D simulation of the Sidoarjo mud on Banjar Panji site. This project used data provided by Lapindo Brantas 
    to simulate the chronology of Sidoarjo mud burst and was to be presented by client to government and parliament.
\end{description}

{\bf Professional Service: Multi-remote Siemens WinCC integration} \hfill {\sl Aug 2011}\\
{\sl Client}: {\bf Perusahaan Gas Negara}\hfill {\sl OPC Specialist}

\vspace{-10pt} 
The project was to integrate multi-stations Siemens Simatic WinCC which were distributed
in different remote locations, South Sumatera and West Java using OPC communication standard.

{\bf Professional Service: WinCC--TOPServer Integration}\hfill {\sl Feb 2007}\\
{\sl Client}: {\bf Yamatake Berca} \hfill {\sl OPC Specialist}

\vspace{-10pt} 
The project was to integrate Siemens Simatic WinCC and Yamatake TOPServer, using OPC
communication standard for a Building Automation project.
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}

{\bf Professional Service: SCADA--Enterprise Integration}\hfill {\sl Feb--Sep 2006}\\
{\sl Client}: {\bf Kaltim Prima Coal} \hfill {\sl OPC Specialist}

\vspace{-10pt} 
The project was to integrate the existing Siemens Simatic WinCC and corporate information system 
(Mincom Minetrak --a mining management solution), which was currently in implementation phase. The
project was using OPC communication standard to stream data from the SCADA system. The
project was im plemented in a live production system which did not tolerate shutdown.
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}

{\bf \uppercase{SIEMENS INDONESIA}--Jakarta, Balikpapan, Handil} \hfill {\sl May 2004--Feb 2006} \\
{\bf MRS-H251 Obsolete ESD and F\&G System Revamping} \hfill {\sl Control System Engineer}

\vspace{-10pt} 
The project was Obsolete ESD and F\&G System Revamping in a plant operated by \textit{Total E\&P
Indonesie} - East Kalimantan. The objective is to revamp shutdown system which was handled by
ALSPHA and implement Siemens technology for the function. The project was also to integrate the
system being implement to the existing system which was Honeywell DCS.

It was a project with a \emph{distinctive level of difficulties and risks} due to the involvment of a live
production system and diverse technologies. This project employed various technologies such as OPC (\textit{\href{https://opcfoundation.org}{OLE for Process Control}}), redundancy
support, failsafe and others. End result of the individual work here was an OPC sub-system which
bridging communication between Siemens Simatic WinCC and Honeywell APPNode which conform
to both communication and safety standard.
\begin{center}
	\rule{0.5\textwidth}{.2pt}
\end{center}

{\bf \uppercase{SELF EMPLOYED}--Jakarta} \hfill {\sl 2000--Dec 2004} \\
Running self-owned internet cafe \& gaming center \hfill {\sl Business Owner}
\vspace{-10pt} 

with allaround services such as printing services, photo-editing, banner \& commercial design, billing system development, computer repair etc.

%----------------------------------------------------------------------------------------
\begin{center}
	\rule{0.5\textwidth}{1pt}
\end{center}
%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTERESTS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
coding, math, guitar \& basses, woodworking, gardening
\end{center} 

%----------------------------------------------------------------------------------------
\end{resume} 

\end{document}